PANCHANGE_analysis

### 2020-08-25 PANCHANGE_analysis.Rmd
vectors with sum scores

@@

## GAD
```{r}
dat.gad <- dat.raw %>%
  drop_na(
  ) %>%
  filter(
    (data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data")
  )

@@

control_numeric == 1 ~ 0,
depressive_disorders_numeric == 1 ~ 1,
anxiety_disorders_numeric == 1 ~ 2,
mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
eating_disorders_numeric == 1 ~ 4,
obsessive_compulsive_disorders_numeric == 1 ~ 5,
mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
mhd.personality_disorder_numeric == 1 ~ 7,
mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 8,
mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
psychotic_disorders_numeric == 1 ~ 10

psychotic_disorders_numeric == 1 ~ 10
mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 8,
mhd.personality_disorder_numeric == 1 ~ 7,
mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
obsessive_compulsive_disorders_numeric == 1 ~ 5,
eating_disorders_numeric == 1 ~ 4,
mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
anxiety_disorders_numeric == 1 ~ 2,
depressive_disorders_numeric == 1 ~ 1,
control_numeric == 1 ~ 0,

```{r Psychiatric disorders hierarchy}
dat <- dat %>%
  mutate(
    Disorder_numeric =
      case_when(
        psychotic_disorders_numeric == 1 ~ 11,
        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 10,
        mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 9,
        mhd.personality_disorder_numeric == 1 ~ 8,
        mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 7,
        obsessive_compulsive_disorders_numeric == 1 ~ 6,
        eating_disorders_numeric == 1 ~ 5,
        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
        (anxiety_disorders_numeric == 1 &
        depressive_disorders_numeric == 1) ~ 3,
        anxiety_disorders_numeric == 1 ~ 2,
        depressive_disorders_numeric == 1 ~ 1,
        control_numeric == 1 ~ 0
      )
  )

dat <- dat %>%
  mutate(
    Disorder =
      recode_factor(
        Disorder_numeric,
        `0` = "Controls",
        `1` = "Depressive disorders",
        `2` = "Anxiety disorders",
        `3` = "Depressive & anxiety disorders",
        `4` = "PTSD",
        `5` = "Eating disorders",
        `6` = "OCDs",
        `7` = "ADHD",
        `8` = "Personality disorders",
        `9` = "Autism",
        `10` = "Bipolar disorders",
        `11` = "Psychotic disorders"
      )
  )

dat %>%
  freq(Disorder)
```

Investigate NAs 
Ask Leo?
```{r NAs in diagnosis}
dat %>%
  filter(is.na(Disorder)) %>%
  freq(Sample)
```

@@

+++ADD CHUNK FOR AGE CATEGORIES HERE
```{r Age categories}

# Psychiatric disorders
```{r vector with psychiatric disorders}
disorder_columns <- c(
    "depressive_disorders_numeric",
    "anxiety_disorders_numeric",
    "eating_disorders_numeric",
    "obsessive_compulsive_disorders_numeric",
    "psychotic_disorders_numeric",
    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
    "mhd.attention_deficit_hyperactivity_disorder_numeric",
    "mhd.personality_disorder_numeric",
    "control_numeric"
)
```

```{r gather to long format Disorder}
dat.long.psych <- dat %>%
  gather(
    key = "Disorder_inc_raw",
    value = "Diagnosis",
    all_of(disorder_columns)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    all_of(diff_score_cols),
    Disorder_inc_raw,
    Diagnosis
  ) %>%
  mutate(Disorder_inc =
           recode_factor(
             Disorder_inc_raw,
             anxiety_disorders_numeric = "Anxiety disorders",
             depressive_disorders_numeric = "Depressive disorders",
             eating_disorders_numeric = "Eating disorders",
             obsessive_compulsive_disorders_numeric = "OCDs",
             psychotic_disorders_numeric = "Psychotic disorders",
             mhd.mania_hypomania_bipolar_or_manicdepression_numeric = "Bipolar disorders",
             mhd.posttraumatic_stress_disorder_ptsd_numeric = "PTSD",
             mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric = "Autism",
             mhd.attention_deficit_hyperactivity_disorder_numeric = "ADHD",
             mhd.personality_disorder_numeric = "Personality disorders",
             control_numeric = "Controls"
           ))

@@

@@

# highest_education
```{r highest_education per Sample}
dat %>%
  count(highest_education, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

# Key worker status
```{r Key worker status per sample}
dat %>%
  count(key_worker, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

@@

@@

```{r gad gather to long format Time_points}
dat.long.gad.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "gad.diff_score",
    all_of(gad.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Disorder,
    Time_point_raw,
    gad.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

```{r gad percentage plot retro_prepan, fig.height=6, fig.width=10}
dat.long.gad.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder")
```

```{r gad plot retro_prepan diff}
dat.long.gad.diff %>%
  filter(Time_point == "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Retrospective"))
```

@@

```{r phq gather to long format Time_points}
dat.long.phq.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "phq.diff_score",
    all_of(phq.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Disorder,
    Time_point_raw,
    phq.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

```{r phq percentage plot retro_prepan}
dat.long.phq.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference phq7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

@@

```{r phq percentage plot retro_prepan, fig.height=6, fig.width=10}
dat.long.phq.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference PHQ9 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder")
```

@@

```{r ocir gather to long format Time_points}
dat.long.ocir.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "ocir.diff_score",
    all_of(ocir.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Disorder,
    Time_point_raw,
    ocir.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "ocir.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

```{r ocir percentage plot retro_prepan, fig.height=6, fig.width=10}
dat.long.ocir.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference OCI-R score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder")
```

@@

Model 0a: Disorders
```{r}
model0a <- lm(
  formula = phq.diff_score_base_prepan ~ Disorder,
  data = dat)

Model 0b: Disorders
```{r}
model0b <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    mhd.autism_aspergers_or_autistic_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat)

Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}
model1 <- lm(
  formula = phq.diff_score_base_prepan ~ Disorder + Gender + Age + Ethnicity + time_diff_sign_up_coping,
  data = dat)

@@

>>>>

```{r}
dat.raw %>%
  freq(Sample)
```

@@

# Vectors for sum_score
```{r Vectors with sum_score_cols}
sum_score_cols <- dat %>%
  select(contains("sum_score")) %>%
  select(-ends_with("raw")) %>%
  colnames()

sum_score_cols

phq.sum_score_cols <- dat %>%
  select(contains("phq")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  select(-contains("8items")) %>%
  colnames()

phq.sum_score_cols

gad.sum_score_cols <- dat %>%
  select(contains("gad")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

gad.sum_score_cols

ocir.sum_score_cols <- dat %>%
  select(contains("ocir")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

ocir.sum_score_cols
```

@@

control_numeric == 1 ~ 0,
depressive_disorders_numeric == 1 ~ 1,
anxiety_disorders_numeric == 1 ~ 2,
mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
eating_disorders_numeric == 1 ~ 4,
obsessive_compulsive_disorders_numeric == 1 ~ 5,
mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
mhd.personality_disorder_numeric == 1 ~ 7,
autism_spectrum_disorder_numeric == 1 ~ 8,
mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
psychotic_disorders_numeric == 1 ~ 10

psychotic_disorders_numeric == 1 ~ 10
mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
autism_spectrum_disorder_numeric == 1 ~ 8,
mhd.personality_disorder_numeric == 1 ~ 7,
mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
obsessive_compulsive_disorders_numeric == 1 ~ 5,
eating_disorders_numeric == 1 ~ 4,
mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
anxiety_disorders_numeric == 1 ~ 2,
depressive_disorders_numeric == 1 ~ 1,
control_numeric == 1 ~ 0,

```{r Psychiatric disorders hierarchy}
dat <- dat %>%
  mutate(
    Disorder_hierarchical_numeric =
      case_when(
        psychotic_disorders_numeric == 1 ~ 11,
        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 10,
        autism_spectrum_disorder_numeric == 1 ~ 9,
        mhd.personality_disorder_numeric == 1 ~ 8,
        mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 7,
        obsessive_compulsive_disorders_numeric == 1 ~ 6,
        eating_disorders_numeric == 1 ~ 5,
        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
        (anxiety_disorders_numeric == 1 &
        depressive_disorders_numeric == 1) ~ 3,
        anxiety_disorders_numeric == 1 ~ 2,
        depressive_disorders_numeric == 1 ~ 1,
        control_numeric == 1 ~ 0
      )
  )

dat <- dat %>%
  mutate(
    Disorder_hierarchical =
      recode_factor(
        Disorder_hierarchical_numeric,
        `0` = "Controls",
        `1` = "Depressive disorders",
        `2` = "Anxiety disorders",
        `3` = "Depressive & anxiety disorders",
        `4` = "PTSD",
        `5` = "Eating disorders",
        `6` = "OCDs",
        `7` = "ADHD",
        `8` = "Personality disorders",
        `9` = "Autism",
        `10` = "Bipolar disorders",
        `11` = "Psychotic disorders"
      )
  )

dat %>%
  freq(Disorder_hierarchical)
```

Investigate NAs 
Ask Leo?
```{r NAs in diagnosis}
dat %>%
  filter(is.na(Disorder_hierarchical)) %>%
  freq(Sample)
```

@@

+++ ADD AGE PLOT HERE

+++ADD CHUNK FOR AGE CATEGORIES HERE
```{r Age categories}
dat %>%
  freq(age_category_full)
```

+++ADD CHUNK FOR AGE CATEGORIES HERE
```{r Age categories}
dat %>%
  group_by(Sample) %>%
  count(age_category_full, Sample)
```

# Psychiatric disorders
```{r vector with psychiatric disorders}
disorder_columns <- c(
    "depressive_disorders_numeric",
    "anxiety_disorders_numeric",
    "eating_disorders_numeric",
    "obsessive_compulsive_disorders_numeric",
    "psychotic_disorders_numeric",
    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
    "autism_spectrum_disorder_numeric",
    "mhd.attention_deficit_hyperactivity_disorder_numeric",
    "mhd.personality_disorder_numeric",
    "control_numeric"
)
```

```{r gather to long format Disorder_hierarchical}
dat.long.psych <- dat %>%
  gather(
    key = "Disorder_inc_raw",
    value = "Diagnosis",
    all_of(disorder_columns)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    all_of(diff_score_cols),
    Disorder_inc_raw,
    Diagnosis
  ) %>%
  mutate(Disorder_inc =
           recode_factor(
             Disorder_inc_raw,
             anxiety_disorders_numeric = "Anxiety disorders",
             depressive_disorders_numeric = "Depressive disorders",
             eating_disorders_numeric = "Eating disorders",
             obsessive_compulsive_disorders_numeric = "OCDs",
             psychotic_disorders_numeric = "Psychotic disorders",
             mhd.mania_hypomania_bipolar_or_manicdepression_numeric = "Bipolar disorders",
             mhd.posttraumatic_stress_disorder_ptsd_numeric = "PTSD",
             autism_spectrum_disorder_numeric = "Autism",
             mhd.attention_deficit_hyperactivity_disorder_numeric = "ADHD",
             mhd.personality_disorder_numeric = "Personality disorders",
             control_numeric = "Controls"
           ))

@@

# Ethnicity
```{r Ethnicity per Sample}
Ethnicity_by_Sample <- dat %>%
  group_by(Sample) %>%
  count(Ethnicity, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

# highest_education
```{r highest_education per Sample}
dat %>%
  group_by(Sample) %>%
  count(highest_education, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

# Key worker status
```{r Key worker status per sample}
dat %>%
  group_by(Sample) %>%
  count(key_worker, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

@@

# Create data set per cohort

## GAD
```{r}
dat.gad <- dat %>%
#  drop_na() %>%
  filter(
    (data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data")
  )

@@

```{r gad gather to long format Time_points gad.diff_score}
dat.long.gad.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "gad.diff_score",
    all_of(gad.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Disorder_hierarchical,
    Time_point_raw,
    gad.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

```{r gad percentage plot retro_prepan, fig.height=6, fig.width=10}
dat.long.gad.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

```{r gad plot retro_prepan diff}
dat.long.gad.diff %>%
  filter(Time_point == "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nRetrospective vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic"))
```

@@

```{r phq gather to long format Time_points}
dat.long.phq.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "phq.diff_score",
    all_of(phq.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Disorder_hierarchical,
    Time_point_raw,
    phq.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

```{r phq percentage plot retro_prepan}
dat.long.phq.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference PHQ9 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

@@

```{r phq percentage plot retro_prepan, fig.height=6, fig.width=10}
dat.long.phq.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference PHQ9 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

@@

```{r ocir gather to long format Time_points}
dat.long.ocir.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "ocir.diff_score",
    all_of(ocir.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Disorder_hierarchical,
    Time_point_raw,
    ocir.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "ocir.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

```{r ocir percentage plot retro_prepan, fig.height=6, fig.width=10}
dat.long.ocir.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference OCI-R score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder_hierarchical")
```

@@

@@

Model 0a: Disorder_hierarchical
```{r Model 0a: Disorder_hierarchical}
model0a <- lm(
  formula = gad.diff_score_base_prepan ~ Disorder_hierarchical,
  data = dat.gad)

Model 0b: Disorders
```{r}
model0b <- lm(
  formula = ocir.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat)

Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}
model1 <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender + age_category_full + Ethnicity + time_diff_sign_up_coping,
  data = dat)

Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}
model1 <- lm(
  formula = pcl.diff_score_base_prepan ~ Disorder_hierarchical + Gender + age_category_full + Ethnicity + time_diff_sign_up_coping,
  data = dat)
